Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-08-16 reports/rmarkdown/01_data_pre_processing.Rmd

# create genus lacto taxonomy
genus_lacto.fun <- function(df){
  genus_lacto <- df %>%
    mutate(Genus_lacto = .$Genus, .after=Seq_ID) %>% 
    mutate(Genus_lacto = ifelse(grepl("crispatus",.$Species), paste(.$Genus_lacto, "crispatus/acidophilus"), 
                                ifelse(grepl("reuteri",.$Species), paste(.$Genus_lacto, "reuteri/oris/frumenti/antri"),
                                  ifelse(grepl("gasseri",.$Species), paste(.$Genus_lacto,"gasseri/johnsonii/taiwanensis"),
                                    ifelse(grepl("murinus",.$Species), paste(.$Genus_lacto,"murinus/animalis/apodemi/salivarius"),
                                      ifelse(grepl("plantarum",.$Species), 
                                           paste(.$Genus_lacto, "plantarum/fabifermentans/composti/paraplantarum/graminis/fuchuensis"),
                                        ifelse(grepl("Lactobacillus",.$Genus), paste(.$Genus, .$Species), 
                                              as.character(.$Genus_lacto))))))) )
  return(genus_lacto)
}

@@

#arrange all datasets to have the same rownames with all bacteria
common_microbes_fun <- function(x) {
  t <- bind_rows(temp) %>%
    select(Taxonomy) %>%
    unique() %>%
    left_join(x, by="Taxonomy") %>%
    mutate(across(everything(), ~replace_na(.x, 0))) %>%
    column_to_rownames(var = "Taxonomy")
  return(t)
}
datasets_ <- map(temp, ~common_microbes_fun(.x))
lapply(datasets_,dim)

@@

>>>>

# create genus lacto taxonomy
genus_lacto.fun <- function(df){
  genus_lacto <- df %>%
    mutate(Genus_lacto = .$Genus, .after=Seq_ID) %>% 
    mutate(Genus_lacto = ifelse(grepl("crispatus",.$Species), paste("L.", "crispatus/acidophilus"), 
                                ifelse(grepl("reuteri",.$Species), paste("L.", "reuteri/oris/frumenti/antri"),
                                  ifelse(grepl("gasseri",.$Species), paste("L.","gasseri/johnsonii/taiwanensis"),
                                    ifelse(grepl("murinus",.$Species), paste("L.","murinus/animalis/apodemi/salivarius"),
                                      ifelse(grepl("plantarum",.$Species), 
                                           paste("L.", "plantarum/fabifermentans/composti/paraplantarum/graminis/fuchuensis"),
                                        ifelse(grepl("Lactobacillus",.$Genus), paste("L.", .$Species), 
                                              as.character(.$Genus_lacto))))))) )
  return(genus_lacto)
}

@@

#arrange all datasets to have the same rownames with all bacteria
common_microbes_fun <- function(x) {
  t <- bind_rows(temp) %>%
    select(Taxonomy) %>%
    unique() %>%
    left_join(x, by="Taxonomy") %>%
    mutate(across(Taxonomy, ~replace_na(.x, "Not assigned"))) %>%
    mutate(across(-Taxonomy, ~replace_na(.x, 0))) %>%
    column_to_rownames(var = "Taxonomy")
  return(t)
}
datasets_ <- map(temp, ~common_microbes_fun(.x))
lapply(datasets_,dim)

@@

# raw files
n <- c("ASV_CVL_V3", "ASV_tissue_V3", "ASV_CVL_V2")
map2(datasets[1:3],n,  ~write.csv(.x, file=paste0(PATH,"results/",.y,"_raw_counts.csv"),row.names = T) )

### 2021-08-16 reports/rmarkdown/03_integrated_datasets.Rmd

```{r Setup, echo = FALSE}
knitr::opts_chunk$set(fig.width  = 10,
                      results    = "hide",
                      message    = FALSE,
                      warning    = FALSE)
```

@@

```{r, echo = FALSE}
library(igraph)
library(rafalib)
library(fgsea)
library(scales)
remotes::install_github("czarnewski/niceRplots",upgrade = "always",force = T)
library(niceRplots)
```

@@

```{r, echo = FALSE}
PATH <- "../../" #Path to the data

#color palettes
pal <- c(RColorBrewer::brewer.pal(9,"Set1"),RColorBrewer::brewer.pal(8,"Set2"),
         RColorBrewer::brewer.pal(9,"Pastel1"),RColorBrewer::brewer.pal(8,"Pastel2")) #color pallete for plots
heat_pal <- c("#000000", colorRampPalette(c("#000000","grey5","grey30","orange3","yellow","yellow","white"))(90))
cor_pal <- colorRampPalette(c("navy","white","firebrick"))(90)

@@

```{r, echo = FALSE}
# Load metadata
metadata <- read.csv(paste0(PATH,"/data/Clinical_visit_2_3_updatefeb22.csv"))
rownames(metadata) <- as.character(metadata$ID)

@@

#import datasets and return matrix with taxa-level resolution
datasets <- lapply(dataset_names, function(x){
  x <- read.csv( paste0(PATH,"results/",x,".csv"),row.names = 1)
  return(as.matrix(x)) })
names(datasets) <- dataset_names

#fill all samples with 0s to make plotting easier
datasets_all_samples <- lapply(datasets, function(x) {
  temp <- matrix(0,nrow = nrow(x),
                 ncol = nrow(metadata),
                 dimnames = list(rownames(x),rownames(metadata)))
  temp[rownames(x),colnames(x)] <- x
  return(temp)
})
lapply(datasets_all_samples,dim)
```

@@

samples_to_use <- colnames(counts)[counts[c(3),] != 0]
datasets_all_samples <- lapply( datasets_all_samples , function(x) { x [ , samples_to_use] } )
metadata <- metadata[ samples_to_use , ]

@@

#Graph construction  
k <- 10 # k for KNN
p <- 0.1 # prunning threshold of SNN

@@

metadata$joint_clustering <- cl$membership
set.seed(1)
U <- uwot::umap(adj,n_neighbors = 30)
h <- hclust(as.dist(adj),method = "ward.D2")
# metadata$joint_clustering <- cutree(h,k = 5)
write.csv2(metadata,"../../results/metadata_integration.csv",row.names = T)

@@

plot( g , vertex.label.cex=0.000001 , vertex.color = pal[factor(metadata$group_M4_CVLv3)] , 
      edge.width=  ( E(g)$weight / max(E(g)$weight)) ,layout=l,
      vertex.size=10,main="FR embedding",
      edge.color=colorRampPalette(c("grey95","black"))(90) [ round( E(g)$weight / max(E(g)$weight) * 88 )+1 ] )
plot( g , vertex.label.cex=0.000001 , vertex.color = pal[factor(metadata$group_M4_CVLv3)] , 
      edge.width=  ( E(g)$weight / max(E(g)$weight)) ,layout=U,
      vertex.size=10,main="umap",
      edge.color=colorRampPalette(c("grey95","black"))(90) [ round( E(g)$weight / max(E(g)$weight) * 88 )+1 ] )
empty_plot()
legend("topleft",title = "Patient groups\ngroup_M4_CVLv3",
       legend = levels(factor(metadata$group_M4_CVLv3)),
       bty = "n",pch = 21,pt.bg = pal,pt.cex = 1.2,xpd=T)
# title("Louvain clusters",cex.main=1,font.main=1)

@@

```{r}
mypar(mar=c(2,15,2,2))

barlist( data = rbind( detected_counts),main = "detected features",
         genes = c(rownames(detected_counts)),labels = sub("_norm.*","",rownames(counts)),
         clustering = metadata$joint_clustering,
         col=pal,draw_mean_lines=F)
add_letter("b")

barlist( data = all_microbiome, main = "detected features",
         genes = c("Gardnerella vaginalis",
                   "Lactobacillus iners",
                   "Lactobacillus jensenii",
                   "Lactobacillus crispatus/acidophilus",
                   "Prevotella amnii",
                   "Prevotella timonensis",
                   "Atopobium vaginae"),
         clustering = metadata$joint_clustering,
         col=pal,draw_mean_lines=F)

@@

```{r, echo = FALSE,fig.width=5,fig.height=5}
x <- datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]]
xL <- rowsum(x , grepl("Lactobacillus",rownames(x)) )[2,] / sum(grepl("Lactobacillus",rownames(x)))
xM <- rowsum(x , grepl("Mobiluncus",rownames(x)) )[2,] / sum(grepl("Mobiluncus",rownames(x)))
xG <- rowsum(x , grepl("Gardnerella",rownames(x)) )[2,] / sum(grepl("Gardnerella",rownames(x)))

@@

mypar(3,1,mar=c(2,6,2,2))
barlist( data = rbind(  BV=mL ,
                        counts_16S=xL),
         main = "Lactobacillus",
         genes = c("BV","counts_16S"),
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal)

barlist( data = rbind(  BV=mM ,
                        counts_16S=xM),
         main = "Monbilicus",
         genes = c("BV","counts_16S"),
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal)

barlist( data = rbind(  BV=mG ,
                        counts_16S=xG),
         main = "Gardanerella",
         genes = c("BV","counts_16S"),
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal)
```

@@

```{r, eval=F,echo = FALSE,fig.width=10,fig.height=4}
myletters <- letters

@@

```{r, eval=F,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])
datasets <- factor(c( rep("tissue_v3",ncol(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]])) , rep("CVL_v3",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) , rep("CVL_v2",ncol(datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

```{r, eval=F,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])
datasets <- factor(c( rep("CVL_v3",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) , rep("CVL_v2",ncol(datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

```{r, eval=F,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])
datasets <- factor(c( rep("tissue_v3",ncol(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]])) , rep("CVL_v3",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

```{r, echo = FALSE}
groupings <- lapply( names(datasets_all_samples)[-1] ,function(x){
  x <- read.csv2( paste0(PATH,"results/Sample_Louvain_clusters_",x,".csv"),row.names = 1 ) })
names(groupings) <- names(datasets_all_samples)[-1]
all_names <- unique(unlist(lapply(groupings,function(x)rownames(x))))

groupings_all_samples <- lapply(groupings,function(x){
  df <- data.frame(group=rep("NA",length(all_names)), row.names = all_names,stringsAsFactors = F)
  df[rownames(x),1] <- as.character(x[,1])
  return(df)
})
names(groupings_all_samples) <- names(groupings)

df <- as.data.frame(groupings_all_samples)
colnames(df) <- paste0( "louvain_",sub( "ASV_","",  sub( "_norma.*","", names(groupings_all_samples) )))
metadata <- cbind(metadata,df[rownames(metadata),])
```

@@

@@

```{r, echo = FALSE,fig.width=8,fig.height=8}
metadata_parameters <- c("Antibiotics","Antibiotics_v2","Antibiotics_v3",
                         "Bacterio_KOH_v2","Bacterio_KOH_v3","Bacterio_TV_v3",
                         "BV_Clue_Cells_v2","BV_Clue_Cells_v3",
                         "BV_Diagnosis_v2","BV_Diagnosis_v3",
                         "BV_Lactobacillus_v2","BV_Lactobacillus_v3",
                         "BV_Monbilicus_v2","BV_Monbilicus_v3",
                         "BV_Vaginal_Garda_v2","BV_Vaginal_Garda_v3",
                         "blood_cervix_v2","blood_cervix_v3",
                         "cervical_inflammation_v2","cervical_inflammation_v3",
                         "HIVstatus","Contraception",
                         "CT_v2","CT_v3","regular_partner",
                         "vaginal_douching_v2","vaginal_douching_v3","joint_clustering")

@@

  TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
  bac_dataset <- datasets_all_samples[[i]]
  dge <- read.csv2(paste0(PATH,"/results/DGE_ASV_CVL_V2_normalized_NOT_batch_corrected.csv"),row.names = 1)
  samples_TRX_and_CVL3 <- colnames(counts) [ colSums(counts[c("Tissue_RNAseq_V3_normalized",i),] > 0)==2 ]

@@

```{r, echo = FALSE,fig.width  = 10, fig.height=5}
taxa <- read.csv2("../../results/taxonomy.csv",row.names = 1,stringsAsFactors = F,as.is = T)
taxa[is.na(taxa)] <- "NA"
rownames(cors) %in% rownames(taxa)

@@

for( i in c("group_M4_CVLv3","group_M9_CVLv3","joint_clustering")){
  for( j in c("ASV_tissue_V3_normalized_batch_corrected",
          "ASV_CVL_V3_normalized_batch_corrected",
          "ASV_CVL_V2_normalized_NOT_batch_corrected")){

@@

    barlist(data=module_means_per_dataset[[j]],
            genes=rownames(module_means_per_dataset[[j]]),col=pal,
            labels = paste0("bac.com.",rownames(module_means_per_dataset[[j]])),
            clustering=temp_group, main=paste0(i,"\n", sub("_norm.*","",j)),srt=45)
  }
}
```

@@

```{r, echo = FALSE,fig.width=10,fig.height=8}
write.csv2(metadata,"../../results/metadata_integration.csv",row.names = T)
```

>>>>

```{r Setup, echo = FALSE}
knitr::opts_chunk$set(fig.width  = 10,
                      results    = "hide",
                      message    = FALSE,
                      warning    = FALSE)
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown")
```

@@

```{r, echo = FALSE}
library(igraph)
library(rafalib)
library(fgsea)
library(scales)
remotes::install_github("czarnewski/niceRplots",upgrade = "always",force = T)
library(niceRplots)
library(tidyverse)
```

@@

```{r, echo = FALSE}
PATH <- "../../" #Path to the data
Set1 <- c("#4DAF4A", "#377EB8", "#E41A1C", "#FF7F00", "#984EA3", "#FFFF33", "#A65628", "#F781BF", "#999999")

#color palettes
pal <- c(Set1,RColorBrewer::brewer.pal(8,"Set2"),
         RColorBrewer::brewer.pal(9,"Pastel1"),RColorBrewer::brewer.pal(8,"Pastel2")) #color pallete for plots
heat_pal <- c("#000000", colorRampPalette(c("#000000","grey5","grey30","orange3","yellow","yellow","white"))(90))
cor_pal <- colorRampPalette(c("navy","white","firebrick"))(90)

@@

```{r, echo = FALSE}
# Load meta data
meta <- read.csv(paste0(PATH,"/data/Clinical_visit_2_3_updatefeb22.csv"))
rownames(meta) <- as.character(meta$ID)

@@

#import datasets and return matrix with genus_lacto level resolution
# datasets <- map(dataset_names, 
#                 ~read.csv(paste0(PATH,"results/",.x, ".csv"),row.names = 1)) %>%
#   set_names(., dataset_names)

#fill all samples with 0s to make plotting easier
#x <- datasets[[2]]
# all_samples <- unique(unlist(lapply(datasets,colnames)))
# datasets_all_samples <- lapply(datasets, function(x) {
#   col <- setdiff(all_samples, colnames(x))
#   temp <- tibble(t = rownames(x))  %>% 
#      tibble::add_column(!!!set_names(as.list(rep(0, length(col))),nm=col)) %>% 
#     column_to_rownames(., var = "t") %>% bind_cols(x) 
#   return(temp)
# })

#import datasets and return matrix with genus_lacto level resolution
datasets <- lapply(dataset_names, function(x){
  x <- read.csv( paste0(PATH,"results/",x,".csv"),row.names = 1)
  return(as.matrix(x)) })
names(datasets) <- dataset_names

# Define what samples to use
samples_to_use <- intersect(colnames(datasets[["ASV_CVL_V3_normalized_batch_corrected"]]),
                            colnames(datasets[["Tissue_RNAseq_V3_normalized"]]))

#fill all samples with 0s to make plotting easier
x <- datasets[[1]]
datasets_all_samples <- lapply(datasets, function(x) {
  temp <- matrix(0,nrow = nrow(x),
                 ncol = nrow(meta),
                 dimnames = list(rownames(x),rownames(meta))
                 )
  temp[rownames(x),colnames(x)] <- x
  return(temp)
})
lapply(datasets_all_samples,dim)

# Clean up metadata
tissue_gr <- read.csv(paste0(PATH,"/data/210609_TissuegroupsJune.csv"))
metadata <- meta %>%
  left_join(tissue_gr, by="ID") %>%
  mutate(Luminal_names = ifelse(.$ModifiedM4 == "NonIners", "L. crispatus/jensenii",
                        ifelse(.$ModifiedM4 == "Iners", "L. iners",
                          ifelse(.$ModifiedM4 == "Gard", "Gardnerella",
                            ifelse(.$ModifiedM4 == "Prev", "High diverse", 
                                    "Other")))) ) %>%
  mutate(Luminal_gr = ifelse(.$ModifiedM4 == "NonIners", "L1",
                        ifelse(.$ModifiedM4 == "Iners", "L2", 
                          ifelse(.$ModifiedM4 == "Gard", "L3",
                            ifelse(.$ModifiedM4 == "Prev", "L4", 
                                    "L5")))) ) %>%
  mutate(Tissue_names = ifelse(.$TissuegroupsJune == "Crisp", "L. crispatus/jensenii",
                        ifelse(.$TissuegroupsJune == "Iners", "L. iners", 
                          ifelse(.$TissuegroupsJune == "Gard", "Gardnerella",
                            ifelse(.$TissuegroupsJune == "Prev", "High diverse", 
                                    "Other")))) ) %>%
  mutate(Tissue_gr = ifelse(.$TissuegroupsJune == "Crisp", "T1",
                        ifelse(.$TissuegroupsJune == "Iners", "T2", 
                          ifelse(.$TissuegroupsJune == "Gard", "T3",
                            ifelse(.$TissuegroupsJune == "Prev", "T4", 
                                    "T5")))) ) %>%
  select(ID:Yeast_v3, group_M9_CVLv3, Luminal_names, Tissue_names, Luminal_gr,Tissue_gr)

rownames(metadata) <- as.character(metadata$ID)
```

@@

datasets_all_samples <- lapply( datasets_all_samples , function(x) { x [ , samples_to_use] } )
metadata <- metadata[ samples_to_use , ]

@@

#Graph construction  
k <- 12 # k for KNN
p <- 0.1 # prunning threshold of SNN 0.14

@@

metadata$Louvain_clusters <- cl$membership
metadata$joint_clustering <- metadata$Luminal_gr
metadata$joint_clustering <- factor(metadata$joint_clustering) 
set.seed(1)
U <- uwot::umap(adj,n_neighbors = 30)
h <- hclust(as.dist(adj),method = "ward.D2")
# metadata$joint_clustering <- cutree(h,k = 5)
write.csv2(metadata,"../../results/metadata_integration.csv",row.names = T)

@@

plot( g , vertex.label.cex=0.000001 , vertex.color = pal[factor(metadata$Luminal_gr)] , 
      edge.width=  ( E(g)$weight / max(E(g)$weight)) ,layout=l,
      vertex.size=10,main="FR embedding",
      edge.color=colorRampPalette(c("grey95","black"))(90) [ round( E(g)$weight / max(E(g)$weight) * 88 )+1 ] )
plot( g , vertex.label.cex=0.000001 , vertex.color = pal[factor(metadata$Luminal_gr)] , 
      edge.width=  ( E(g)$weight / max(E(g)$weight)) ,layout=U,
      vertex.size=10,main="umap",
      edge.color=colorRampPalette(c("grey95","black"))(90) [ round( E(g)$weight / max(E(g)$weight) * 88 )+1 ] )
empty_plot()
legend("topleft",title = "Patient groups\nLuminal_gr",
       legend = levels(factor(metadata$Luminal_gr)),
       bty = "n",pch = 21,pt.bg = pal,pt.cex = 1.2,xpd=T)
# title("Louvain clusters",cex.main=1,font.main=1)

@@

```{r}
mypar(mar=c(3.2,15,2,2))

barlist( data = rbind( detected_counts),main = "detected features",
         genes = c(rownames(detected_counts)),labels = sub("_norm.*","",rownames(counts)),
         clustering = metadata$joint_clustering, 
         col=pal[factor(metadata$joint_clustering)],draw_mean_lines=F)
add_letter("b")

barlist( data = all_microbiome, main = "detected features",
         genes = c("Gardnerella",
                   "Lactobacillus iners",
                   "Lactobacillus jensenii",
                   "Lactobacillus crispatus/acidophilus",
                   "Prevotella",
                   "Atopobium"),
         clustering = metadata$joint_clustering,
         col=pal[factor(metadata$joint_clustering)], draw_mean_lines=F) # ,srt = 65
#legend(0,legend = levels(factor(metadata$Luminal_gr)))

# barlist( data = all_microbiome, main = "detected features",
#          genes = c("Gardnerella vaginalis",
#                    "Lactobacillus iners",
#                    "Lactobacillus jensenii",
#                    "Lactobacillus crispatus/acidophilus",
#                    "Prevotella amnii",
#                    "Prevotella timonensis",
#                    "Atopobium vaginae"),
#          clustering = metadata$joint_clustering,
#          col=pal,draw_mean_lines=F)
```

@@

```{r, echo = FALSE,fig.width=5,fig.height=5}
x <- datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]]
xL <- rowsum(x , grepl("L.",rownames(x)) )[2,] / sum(grepl("L.",rownames(x)))
xM <- rowsum(x , grepl("Mobiluncus",rownames(x)) )[2,] / sum(grepl("Mobiluncus",rownames(x)))
xG <- rowsum(x , grepl("Gardnerella",rownames(x)) )[2,] / sum(grepl("Gardnerella",rownames(x)))

@@

mypar(3,1,mar=c(2,6,2,2))
barlist( data = rbind(  BV=mL ,
                        counts_16S=xL),
         main = "Lactobacillus",
         genes = c("BV","counts_16S"),
         clustering = metadata$joint_clustering, #srt = 60,
         draw_mean_lines=F,col = pal[factor(metadata$joint_clustering)])

barlist( data = rbind(  BV=mM ,
                        counts_16S=xM),
         main = "Monbilicus",
         genes = c("BV","counts_16S"), #srt = 60,
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal[factor(metadata$joint_clustering)])

barlist( data = rbind(  BV=mG ,
                        counts_16S=xG),
         main = "Gardnerella",
         genes = c("BV","counts_16S"), #srt = 60,
         clustering = metadata$joint_clustering,
         draw_mean_lines=F,col = pal[factor(metadata$joint_clustering)])
```

@@

```{r, eval=T,echo = FALSE,fig.width=10,fig.height=4}
myletters <- letters

@@

```{r, eval=T,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])
datasets <- factor(c( rep("tissue_v3",ncol(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]])) , rep("CVL_v3",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) , rep("CVL_v2",ncol(datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

```{r, eval=T,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])
datasets <- factor(c( rep("CVL_v3",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) , rep("CVL_v2",ncol(datasets_all_samples[["ASV_CVL_V2_normalized_NOT_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

```{r, eval=T,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])
datasets <- factor(c( rep("tissue_v3",ncol(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]])) , rep("CVL_v3",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

@@

```{r, echo = FALSE}
# groupings <- lapply( names(datasets_all_samples)[-1] ,function(x){
#   x <- read.csv2( paste0(PATH,"results/Sample_Louvain_clusters_",x,".csv"),row.names = 1 ) })
# names(groupings) <- names(datasets_all_samples)[-1]
# all_names <- unique(unlist(lapply(groupings,function(x)rownames(x))))
# 
# groupings_all_samples <- lapply(groupings,function(x){
#   df <- data.frame(group=rep("NA",length(all_names)), row.names = all_names,stringsAsFactors = F)
#   df[rownames(x),1] <- as.character(x[,1])
#   return(df)
# })
# names(groupings_all_samples) <- names(groupings)
# 
# df <- as.data.frame(groupings_all_samples)
# colnames(df) <- paste0( "louvain_",sub( "ASV_","",  sub( "_norma.*","", names(groupings_all_samples) )))
# metadata <- cbind(metadata,df[rownames(metadata),])

Louvain_clusters <- bind_cols(ID = cl$names, louvain_CVL_V3 = cl$membership)

df <- metadata %>%
  left_join(., Louvain_clusters, by="ID")

@@

```{r, echo = FALSE,fig.width=8,fig.height=8}
metadata_parameters <- c("Antibiotics","Antibiotics_v2","Antibiotics_v3",
                         "Bacterio_KOH_v2","Bacterio_KOH_v3","Bacterio_TV_v3",
                         "BV_Clue_Cells_v2","BV_Clue_Cells_v3",
                         "BV_Diagnosis_v2","BV_Diagnosis_v3",
                         "BV_Lactobacillus_v2","BV_Lactobacillus_v3",
                         "BV_Monbilicus_v2","BV_Monbilicus_v3",
                         "BV_Vaginal_Garda_v2","BV_Vaginal_Garda_v3",
                         "blood_cervix_v2","blood_cervix_v3",
                         "cervical_inflammation_v2","cervical_inflammation_v3",
                         "BV_WBC_v2", "BV_WBC_v3","marital_status",
                         "HIVstatus","Contraception",
                         "CT_v2","CT_v3","regular_partner",
                         "vaginal_douching_v2","vaginal_douching_v3","Luminal_gr", "Tissue_gr", 
                         "Louvain_clusters")

@@

  TRX <- datasets_all_samples[["Tissue_RNAseq_V3_normalized"]]
  bac_dataset <- datasets_all_samples[[i]]
  dge <- read.csv2(paste0(PATH,"results/DGE_ASV_CVL_V2_normalized_NOT_batch_corrected.csv"),row.names = 1)
  samples_TRX_and_CVL3 <- colnames(counts) [ colSums(counts[c("Tissue_RNAseq_V3_normalized",i),] > 0)==2 ]

@@

```{r, echo = FALSE,fig.width  = 10, fig.height=5}
# for Genus_lacto taxonomy:
taxa <- read_csv("../../results/SeqID_to_gen-lacto_tax-oth.csv") %>%
  select(-Sequence, -Seq_ID, -taxa_other, -Species) %>%
  unique() %>%
  filter(!(is.na(.$Genus_lacto))) %>%
  filter(!(.$Genus == "Granulicatella" & .$Family == "Enterococcaceae")) %>%
  column_to_rownames(., var = "Genus_lacto")

# For other_taxa taxonomy:
# taxa <- read.csv2("../../results/taxonomy.csv",row.names = 1,stringsAsFactors = F,as.is = T)
# taxa[is.na(taxa)] <- "NA"
# rownames(cors) %in% rownames(taxa)

@@

for( i in c("Luminal_gr","group_M9_CVLv3","Louvain_clusters")){
  for( j in c("ASV_tissue_V3_normalized_batch_corrected",
          "ASV_CVL_V3_normalized_batch_corrected",
          "ASV_CVL_V2_normalized_NOT_batch_corrected")){

@@

    barlist(data=module_means_per_dataset[[j]],
            genes=rownames(module_means_per_dataset[[j]]),col=pal[factor(temp_group)],
            labels = paste0("bac.com.",rownames(module_means_per_dataset[[j]])),
            clustering=temp_group, main=paste0(i,"\n", sub("_norm.*","",j)),srt=45)
  }
}
```

@@

```{r, echo = FALSE,fig.width=10,fig.height=8}
metadata <- select(metadata, -joint_clustering, -group_M9_CVLv3)
write.csv2(metadata,"../../results/metadata_integration.csv",row.names = T)
```

### 2021-08-16 reports/rmarkdown/manuscript/manuscript_template.tex

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{March 18, 2021}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-3}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-4}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-5}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-6}

>>>>

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{March 19, 2021}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-24-1}

\hypertarget{figure-s14}{%
\subsection{Figure S14}\label{figure-s14}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-25-1}

\hypertarget{figure-s15}{%
\subsection{Figure S15}\label{figure-s15}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-26-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-26-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-26-3}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-26-4}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-26-5}

\begin{center}\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/Print rare curves-1} \end{center}

\textbf{Supp. Figure 10. Rarefraction curves}. \textbf{A} Boston 1 sequencing run, \textbf{B} Sthlm sequencing run and \textbf{C} and \textbf{D} shows Boston sequencing run 2 split in two plots showing the CVL visit 2 samples and the the TISSUE visit 3 samples respectively
